Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-17 ba_resubmit/response_to_reviewers2.tex

	``Consider a data files $A$ and $B$, consisting of records $A_i$ and $B_j$ respectively, where $i \in \{1, \ldots n_A\}$ and $j \in \{1, \ldots n_B\}$".
}

\setcounter{responsectr}{0}
\section{Reviewer Comments}

	\pointRaised{R}{%
	For the missing data treatment now included just before Section 2.1, is the assumption truly missing at random, or missing completely at random? Or, does this distinction not matter because of the independence assumed across elements of the comparison vector?}

	\textcolor{teal}{See two comments below regarding MAR versus MCAR.}

	\textcolor{teal}{Answer for MAR: Yes, the assumption is truly missing at random. This distinction between truly missing at random and missing completely at random does not matter due to two assumptions. Following Sadinle (2017), we assume that the fields in the comparison vectors are conditionally independent given the coreference matrix and we assume that the missing comparisons are ignorable (Sadinle (2017). Therefore, our likelihood is the same as in Sadinle (2017) (see equations (3) and (4) of his paper). As stated by Sadinle (2017), ``we work under the assumption of ignorability of the missingness mechanism for the comparisons so that we can base our inferences on the marginal distribution of the observed comparisons (Little and Rubin, p. 90)."  We refer to Sadinle (2017), Section 4.2, page 604 for further details.}

	\textcolor{teal}{Answer for MCAR: The assumption is missing completely at random due to fact that we assume the fields in the comparison vectors are conditionally independent given the coreference matrix. The assumption is not missing at random as we do not assume that the missing comparisons are ignorable.}

@@

%
%\reply{%
%	We realize that the integration of pi out of the full conditionals is not necessary for our sampler. For clarity, we decided to redo the simulations using a Gibbs sampler that samples $\pi$ from its full conditional, and then samples $Z$ from its full conditionals. We obtained equivalent results, which is unsurprising, because with high numbers of observations, the posterior of the beta distribution is highly concentrated around its mean.
%	
%	Therefore, we have updated the paper with full conditionals for the standard Gibbs sampler. We leave the remark about marginalization in the Appendix to facilitate comparisons to Sadinle's method.
%
%}

\pointRaised{R}{%
	I do not understand the statement just below Equation (10): “When j has no match in $X_1$, we write $(n_1 +j, j) \in h_{P+1}$” My understanding of these patterns is that they are based on observed comparison vectors without consideration of Z (matches). In the second paragraph of Section 4.3, the H notation includes the matches (Z), in notation and definition that seems to conflict with the statement just below Equation (10). This also comes into play in Equation (16)}

	\textcolor{teal}{Comments: Tell the AE they are correct and mention where you correct the confusion. Then move on. (No need to state what you intended). Mention what equations numbers have been updated to help the AE now given the major revision. \textcolor{red}{Please redo this one to answer the question more directly.}}

@@

	\reply{%
	You are correct that the comparison vectors are created (and therefore, patterns are assigned) without regard to $Z$. This notation was created purely to be able to denote when a record was left unlinked during the Gibbs Sampler as in Equation 16 in the submitted draft.

	I can see why this is confusing. Therefore, we have removed that line, and changed the notation for record $B_j$ being unmatched to just be''otherwise".
	}

\pointRaised{R}{%
	Third paragraph of Section 4.1: The authors claim they are computing “sufficient statistics”. What exactly are these statistics sufficient for?
	}

	\textcolor{teal}{Comment: Make it more brief and no need to provide notation when it's not needed.}

	\textcolor{teal}{Thank for pointing out our typo. We have revised the text to state ``summary statistics" instead of ``sufficient statistics."}

@@

	\reply{%
		We show in the revised Section 4.2 that we can write conditional likelihoods  and posterior updates for $\bm{m}$, $\bm{u}$, and $\bm{Z}$ using the statistics in $\tilde{\Gamma} = \{\mathcal{P}, \mathcal{R}, \mathcal{N} \}$. However, we cannot express the full likelihood in (14) through these statistics. Therefore, we have revised to text to say ``summary statistics" instead of  ``sufficient statistics."}

\pointRaised{R}{%
	First paragraph of Section 4.2: The authors state: “Posterior calculations still attribute the appropriate weight to all records through the summary statistics…” What is meant by the term “weight”? Which records are appropriately weighted – those in X2?}

	\textcolor{teal}{Comment: Brian, you have not answered the reviewer's question regarding what is meant by weight and what records are appropriately weighted. \textcolor{red}{Please revise to directly answer the question in the revised text with equation numbers.}}

	\textcolor{teal}{
	We have revised the ordering of Sections 4.2 and 4.3, so that we first discuss hashing, then posterior inference, then chunkwise computation of the comparison matrix, and then SEI. With this new ordering, and with the newly provided equations 15 -19, we hope that the contribution of \emph{all} record pairs is recorded through the summary statistics in $\mathcal{N}$ is now more clear. 	
	}

@@

\reply{%

	We have switched the order of Sections 4.2 and 4.3, so that we first discuss hashing, then posterior inference, then chunkwise computation of the comparison matrix, and then SEI. With this new ordering, and with the newly provided equations (15 -19) it is clearer that the contribution of \emph{all} record pairs is recorded through the summary statistics in $\mathcal{N}$.
}

\pointRaised{R}{%
	Second paragraph of Section 4.2: “and delete those comparison vectors”. Which are “those” vectors?}

	\reply{

	\textcolor{teal}{``Those comparison vectors" referred to removing the larger (and expensive) $\Gamma^{ab}$ from memory and continuing our calculations with the compressed comparison vectors $\tilde{\Gamma}^{ab}.$ }

	The revised text states: ``\textcolor{teal}{Then, we} conduct hashing, obtain the compressed \textcolor{teal}{comparison vectors} $\tilde{\gamma}^{ab}$, and \textcolor{teal}{remove} the \textcolor{teal}{memory-intensive} \textcolor{teal}{comparison vectors} $\gamma^{ab}$ before continuing with the next chunk of data. See Section 4.3, page 10. 
	}

%\reply{%
%	We have revised that sentence to read ''We then conduct hashing, obtain the compressed $\tilde{\Gamma}^{ab}$ for later calculations, and delete the larger $\Gamma^{ab}$ from memory before continuing with the next chunk of data."
%}

### 2023-07-17 ba_resubmit/kundinger_resubmit2.tex
working on comments for brian.

\begin{abstract}
%Recently, researchers have developed Bayesian versions of the Fellegi-Sunter model for record linkage. These have the crucial advantage of quantifying uncertainty from imperfect linkages.  
Within the field of record linkage, Bayesian methods have the crucial advantage of quantifying uncertainty from imperfect linkages. However, current implementations of Bayesian Fellegi-Sunter models are computationally intensive, making them challenging to use on larger-scale record linkage tasks. To address these computational considerations, we propose fast beta linkage (\texttt{fabl}), an extension to the Beta Record Linkage (\texttt{BRL}) method of \cite{sadinle_bayesian_2017}. Specifically, we use independent prior distributions over the matching space, allowing us to use hashing techniques that reduce computational overhead. This also allows us to complete pairwise record comparisons over large data files through parallel computing and to reduce memory costs through a new technique called storage efficient indexing. Through simulations and two case studies, we show that \texttt{fabl} can have markedly increased speed with minimal loss of accuracy when compared to \texttt{BRL}.
%
%\textcolor{blue}{We propose a variation on Bayesian Fellegi-Sunter models that we call fast beta linkage, or \texttt{fabl}, and is motivated by computational considerations.  Our method extends that of \cite{sadinle_bayesian_2017}, who extended the early work of \cite{fellegi_theory_1969}.}

\end{abstract}

%% ** Keywords **
\begin{keyword}%[class=MSC]
\kwd{bipartite record linkage}
\kwd{entity resolution}
\kwd{data cleaning}
\kwd{parallelization}
\kwd{hashing}
\end{keyword}

@@

% Possible citation for bipartite matching. 
%\citep{fellegi_theory_1969, jaro1989, Winkler1988, belin_A995, larsen_2001, liseo_2011,  herzog2007data, gutman_bayesian_2013, sadinle_bayesian_2017}.

@@

%but this model misspecification can still lead to poor results \citep{sadinle_bayesian_2017}.

@@

%Following the suggestion in \cite{wortman2019}, we relax the one-to-one matching requirement of \texttt{BRL} and use independent priors over the matching space.

@@

%Consider two data files $A$ and $B$, consisting of records $\{A_i: i = 1, \ldots, n_A\}$ and $\{B_j: j = 1, \ldots, n_B\}$. Suppose the files have $F$ fields in common to be used for linkage, and that these fields take on values $A_{if}$ and $B_{jf}$ respectively.

@@

%\subsection{Fellegi-Sunter Models}
%\label{fellegi-sunter}

@@

%Within this framework, record pairs are independently classified as matches and nonmatches based on the estimated parameters. However, such independent classifications often leads to links that violate one-on-one matching assumptions, requiring post-processing to achieve desirable results. To address this issue, \cite{jaro1989} proposed an optimization technique using the estimated model parameters to produce a bipartite matching. \cite{sadinle_bayesian_2017} later showed that this method is equivalent to a maximum likelihood estimate.

%The Fellegi-Sunter method then uses thresholds $T_m$ and $T_u$ such that all record pairs with $w_{ij} > T_m$ are declared as links, and all those with $w_{ij} < T_u$ are declared as non-links (with those such that $T_u < w_{ij} < T_m$ left undetermined and subject to clerical review). This is a problem in practice as transitive closures can be violated. Since each $w_{ij}$ is calculated independently, there can be situations in which both $w_{ij} > T_m$ and $w_{i'j} > T_m$, so both $(i,j)$ and $(i', j)$ are declared as links, even though such a matching is not allowed by assumption.

%To address this issue, \cite{jaro1989} proposed solving the following linear sum assignment problem:
%\begin{align}
%     \label{eqn:jaro}
%     &\max_{\Delta} \sum_{i=1}^{n_A} \sum_{j=1}^{n_B} w_{ij} \Delta_{ij}
%     \quad \text{subject to} \quad \Delta_{ij} \in \{0,1\}; \\
%     & \quad \quad \sum_{i=1}^{n_A}  \Delta_{ij}  \leq 1, j=1,2, \ldots n_B; \; \text{and} \notag\\
%     & \quad \quad\sum_{i=1}^{n_B}  \Delta_{ij}  \leq 1, i=1,2, \ldots n_A. \notag
%\end{align}
%
%The solution to this problem, for which several simple algorithms exist, is a bipartite matching that maximizes the sum of the Fellegi-Sunter weights among matched pairs. Jaro provided no theoretical justification for using this approach; however \cite{sadinle_bayesian_2017} recently showed that under certain conditions, (\ref{eqn:jaro}) is the maximum likelihood estimate for bipartite matching.

%The comparison data $\gamma_{ij}$ are not sufficient to determine whether a record is a match or nonmatch because of errors that naturally occur in the data. This motivated \cite{fellegi_theory_1969} to consider the likelihood ratio
%\begin{align}
%     \label{eqn:wts}
%     w_{ij} = \frac{p(\gamma_{ij} \mid \Delta_{ij} = 1)}{p(\gamma_{ij} \mid \Delta_{ij} = 0)}
%\end{align}
%as a weight to estimate if record pairs are a match or nonmatch. This ratio will be large when there is strong evidence of the pair being a match, and small otherwise.
%
%In practice, $p(\cdot \mid \Delta_{ij} = 1)$ and $p(\cdot \mid \Delta_{ij} = 0)$ are unknown to the modeler, and thus must be estimated.
%
%%is the set of parameters $u_{fl} = p(\gamma_{ij}^f = l|Z_j \neq i)$ for the nonmatching pairs.
%
%After estimating $\bm{m}$ and $\bm{u}$, the Fellegi-Sunter method uses thresholds $T_m$ and $T_u$ such that all record pairs with $w_{ij} > T_m$ are declared as links, and all those with $w_{ij} < T_u$ are declared as non-links (with those such that $T_u < w_{ij} < T_m$ left undetermined and subject to clerical review). This is a problem in practice as transitive closures can be violated. Since each $w_{ij}$ is calculated independently, there can be situations in which both $w_{ij} > T_m$ and $w_{i'j} > T_m$, so both $(i,j)$ and $(i, j')$ are declared as links, even though such a matching is not allowed by assumption.

%\subsection{Beta Record Linkage Model}
%\label{BRL}

%To estimate a one-to-one matching without using a post-processing step, \cite{sadinle_bayesian_2017} incorporated this constraint directly into the model through a prior distribution over the matching space.

%To estimate a one-to-one matching without using a post-processing step, \cite{sadinle_bayesian_2017} incorporates this constraint directly into the model through a

@@

%\begin{table}[t!]
%	\centering
%	\begin{tabular}[t!]{ll}
%		Symbol & Description \\
%		\hline
%		$A, B$ & data files\\
%		$i \in 1, \ldots, n_A $ & index over records in $A$\\
%		$j \in 1, \ldots, n_B $ & index over records in $B$\\
%		$f \in 1, \ldots F$ & index over fields used for comparisons \\
%		$l \in 1, \ldots L_f$ & index over agreement levels for feature $f$ \\
%		$n_{AB}$ & number of matches between $A$ and $B$\\
%		$\gamma_{ij}$ & comparison vector for records $A_i$ and $B_j$ \\
%		$Z_j = i$ & records $A_i$ and $B_j$ match \\
%		$Z_j = n_A + j$ & record $B_j$ has no match in $A$ \\
%		$m_{fl}$ & $p(\gamma_{ij}^f = l | Z_j = i)$ \\
%		$u_{fl}$ & $p(\gamma_{ij}^f = l | Z_j \neq i)$ \\
%		$\pi$ & probability that a record in $B$ has a match in $A$ \\
%		\hline
%	\end{tabular}\caption{Summary of model notation.}\label{table_notation_A}
%\end{table}
%
%For clarity, we present our full model below. A summary of notation is provided in Table \ref{table_notation_A}.
\begin{subequations}
\begin{align}
	\mathcal{L}(\bm{Z}, \bm{m}, \bm{u} \mid \gamma) &= \prod_{i=1}^{n_A}  \prod_{j=1}^{n_B}\prod_{f=1}^{F}\prod_{l=1}^{L_f}\left[  m_{fl}^{I(Z_j = i)}u_{fl}^{I(Z_j \neq i)}\right]^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}, \label{eqn:likelihood}\\
	\bm{m}_f &\sim \text{Dirichlet}(\alpha_{f1}, \ldots, \alpha_{f L_f}), \forall f = 1, \ldots, F, \label{eqn:m} \\
	\bm{u}_f &\sim \text{Dirichlet}(\beta_{f1}, \ldots, \beta_{f L_f}),\forall f = 1, \ldots, F,  \label{eqn:u}\\
	p(Z_j = q| \pi)  &=
	\begin{cases} 
		\frac{1}{n_A}\pi,  & q \leq n_A; \\
		1-\pi, &  q  = n_A + j; \\
	\end{cases} \label{eqn:z}\\
	\pi &\sim \text{Beta}(\alpha_{\pi}, \beta_{\pi})\label{eqn:pi}.
\end{align}
\end{subequations}

%\hypertarget{posterior-sampling}{%
%	\subsection{Gibbs Sampler}
%	\label{gibbs_sampling}}

We estimate the posterior distribution of the parameters in (\ref{eqn:likelihood} - \ref{eqn:pi}) using a Gibbs sampler. We initialize $\bm{m}$ and $\bm{u}$ from random draws from their prior distributions, and initialize $\bm{Z}$ to reflect no matches across data files; that is, $\bm{Z} = (n_A + 1, \ldots, n_A + n_B)$. To take the $(s+1)$th sample of each $\bm{m}_f$ and $\bm{u}_f$ given $\bm{Z}^{(s)}$, we use the full conditionals,
\begin{subequations}
\begin{align}
	\bm{m}_f^{(s+1)}|\gamma, \bm{Z}^{(s)} &\sim \text{Dirichlet}(\alpha_{f1}(\bm{Z}^{(s)}), \ldots, \alpha_{fL_f}(\bm{Z}^{(s)})), \label{eqn:m_update} \\
	\bm{u}_f^{(s+1)}|\gamma, \bm{Z}^{(s)} &\sim \text{Dirichlet}(\beta_{f1}(\bm{Z}^{(s)}), \ldots, \beta_{fL_f}(\bm{Z}^{(s)})), \label{eqn:u_update} \\
	\text{where }\alpha_{fl}(\bm{Z}^{(s)})&= \alpha_{fl} + \sum_{i=1}^{n_A}\sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} = i), \label{eqn:alpha_update} \\
	\text{and } \beta_{fl}(\bm{Z}^{(s)})&=  \beta_{fl} + \sum_{i=1}^{n_A}\sum_{j=1}^{n_B}  I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} \neq i) \label{eqn:beta_update}.
	%where $\alpha_{fl}(\bm{Z}^{(s)})= \alpha_{fl} + \sum_{i,j} I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} = i)$, and $\beta_{fl}(\bm{Z}^{(s)})= \\ \beta_{fl} + \sum_{i,j} I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} \neq i)$.
\end{align}
\end{subequations}
Next, the full conditional for $\pi$ is given by
\begin{align}
	\pi^{(s+1)}|\bm{Z}^{(s)},  \alpha_{\pi}, \beta_{\pi}, \pi \sim  \text{Beta}(n_{AB}(\bm{Z}^{(s)}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}^{(s)}) + \beta_{\pi}).
\end{align}
where $n_{AB}(\bm{Z}^{(s)}) = \sum_{j=1}^{n_B} I(Z_j^{(s)} \leq n_A)$.

Lastly, we sample $\bm{Z}$ componentwise from the full conditional for each $Z_j$:
\begin{align}
	\label{eqn:z_full_conditional}
	p\left(Z_j^{(s+1)}  = q|\gamma, \bm{m}^{(s+1)}, \bm{u}^{(s+1)},  \pi^{(s+1)}\right) \propto
	\begin{cases} 
		\frac{\pi^{(s+1)}}{n_A} w_{qj}^{(s+1)},  & q \leq n_A; \\
		1 - \pi^{(s+1)}, & q  = n_A + j, \\
	\end{cases}
\end{align}
%\begin{align}
%\label{eqn:z_full_conditional}
%p\left(Z_j^{(s+1)}  = z_j|\gamma, \bm{m}^{(s+1)}, \bm{u}^{(s+1)}, \bm{Z^{(s)}}\right) \propto
%\begin{cases} 
%	w_{z_j, j}^{(s+1)},  & z_j \leq n_A; \\
%	n_A \frac{n_B - n_{AB}(\bm{Z}^{(s)}) + \beta_{\pi}}{n_{AB}(\bm{Z}^{(s)}) + \alpha_{\pi}}, & z_j  = n_A + j, \\
%\end{cases}
%\end{align}
where, for all $i \in \{1, \ldots, n_A\}$ and $j \in \{1, \ldots, n_B\}$, 
\begin{align}
	\label{eqn:fs_weight}
	w_{ij}^{(s)} = \prod_{f=1}^{F}\prod_{l = 1}^{L_f} \left(\frac{m_{fl}^{(s)}}{u_{fl}^{(s)}}\right)^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}.
\end{align}
Derivations for these full conditionals can be found in Appendix \ref{app:derivations}.

@@

With \texttt{fabl}, we introduce two techniques to further expand the scalability of probabilistic record linkage. First, we propose hashing methods that allow us to compute summary statistics that reduce the computational complexity of the Gibbs sampler and the memory requirements of the storing the comparison vectors. Second, we introduce storage efficient indexing, which reduces the memory costs associated with unlikely matches. 
%For convenience, Table \ref{table_notation_B} summarizes the notation introduced throughout this section.

%\begin{table}[t!]
%	\centering
%	\begin{tabular}[t!]{ll}
%		Symbol & Description \\
%		\hline
%		$P$ & number of agreement patterns exhibited in $\gamma$ \\
%		$h_p$ & agreement pattern $p$ \\
%		$e(h_p)$ & one-hot encoding of agreement pattern $p$ \\
%		$\gamma_{ij} = h_p$ & comparison vector between records $A_i$ and $B_j$ exhibits pattern $p$ \\
%		$r_{p_j}$ & list of records in $A$ that share agreement pattern $p$ with record $B_j$ \\
%		$N_{p_j}$ & number of records in $A$ that share agreement pattern $p$ with record $B_j$ \\
%		$N_p^m$ & number of matching comparison vectors that exhibit pattern $p$ \\
%		$N_p$ & number of total comparison vectors that exhibit pattern $p$ \\
%
%		\hline
%	\end{tabular}\caption{Summary of hashing notation.}\label{table_notation_B}
%\end{table}

@@

We then map these integers to sequential integers $\{1, \ldots, P\}$. We refer to each unique agreement pattern as $h_p$, and to the set of unique agreement patterns as $\mathcal{P} = \{h_1, \ldots, h_P\}$. When the $(i,j)$ record pair exhibits agreement pattern $p$, we say $\gamma_{ij} = h_p$. In calculations, we will at times use the one-hot encoding of agreement pattern $h_p$, denoted $e(h_p)$. This is a vector of length $\sum_{f=1}^F L_f$ in which the $l + \sum_{k=1}^{f-1} L_k$ component is 1 when $\gamma_{ij}^f = l$, and 0 otherwise. 
%A more complete example of the one-hot encoding is provided in Appendix \ref{app:ohe}.

@@

		For linkage tasks with large amounts of records, we can partition $A$ and $B$ into $t_A$ and $t_B$ smaller disjoint chunks for more manageable computations. Let $\{A^1, \dots, A^{t_A}\}$ be a partition of $A$ such that $\cup_{a=1}^{t_A} A^a = A$ and $A^a \cap A^{a'}=\emptyset$ for all $a \neq a'$.  Likewise, let $\{B^1, \dots, B^{t_b}\}$ be a partition of $B$ such that $\cup_{b=1}^{t_B} B^b = B and B^b \cap B^{b'}=\emptyset$ for all $b \neq b'$.  For example, if $n_A = n_B = 50000$ and $t_A = t_B = 100$, each $A^a$ and $B^b$ would contain disjoint sets of 500 records. For each $A^a$, we conduct all-to-all comparisons with each $B^b$ to construct the comparison matrix $\gamma^{ab}$. We then conduct hashing, obtain the compressed $\tilde{\gamma}^{ab}$, and delete the larger $\gamma^{ab}$ from memory before continuing with the next chunk of data. In detail, we calculate
\begin{subequations}
	\begin{align}
		r_{p_j}^{ab} &= \{i \in 1, \dots, n_A| \gamma_{ij} = h_p, j \in B^b\}, \label{r_{p_j}^{ab}} \\
		N_{p_j}^{ab} &= |r_{p_j}^{ab}|. \label{N_{p_j}^{ab}}
	\end{align}
\end{subequations}
These can computed serially or in parallel. Summary statistics from each pairwise chunk comparison can be synthesized to recover summary statistics for the full comparison matrix $\gamma$ through
\begin{subequations}
	\begin{align}
		r_{p_j} &= (r_{p_j}^{11}, \ldots, r_{p_j}^{ t_A t_B}) \text{ for } a = 1, \ldots, t_A \text{ and } b = 1, \ldots, t_B, \label{r_{p_j}} \\
		N_{p_j} &= \sum_{a = 1}^{t_A} \sum_{b = 1}^{t_B} N_{p_j}^{ab}.\label{N_{p_j}}	\end{align}
\end{subequations}

@@

%	We simulate these data for different values of $n_A$ and $n_B$, always with $n_B/2$ records in common across data files. and compare the run-time of \texttt{fabl} against \texttt{BRL}. Since we have 5 binary comparison fields, the number is unique patterns $P$ is bounded above by $2^5 = 32$, a bound which is consistently attained in simulations with more records.

	 %\textcolor{blue}{DELETE? The $\bm{u}$ parameters are chosen to emulate what is seen in practice for first name, last name, day of birth, and month of birth. The parameters for year would vary largely by context, so we choose them here to adjust the desired difficulty of the linkage task.}

@@

Although the figures suggest that $S=2$ is adequate for maintaining linkage performance, we suggest a more conservative value like $S=10$. When evaluating the performance of a record linkage algorithm, researchers often examine posterior probabilities. By concentrating probability mass on arbitrary nonmatches, low values of $S$ may induce suspiciously high posterior probability for certain record pairs, providing a misleading perception of model performance. 
%We want to be sure that the set of records pairs exhibiting agreement patterns that have considerable probability of matching do not get reduced through SEI.

%\begin{figure}[t]
%	\begin{center}
%		\includegraphics[width=0.6\textwidth]{../SEI_sensitivity/Z_plot}
%		\caption{Distinct values of $\hat{Z}$ in Section \ref{SEI-sensitivity} simulation.}
%		\label{fig:SEI_Z}
%	\end{center}
%\end{figure}
%
%\begin{figure}[t]
%	\begin{center}
%		\includegraphics[width=0.6\textwidth]{../SEI_sensitivity/eval_plot} 
%		\caption{Means and 95\% credible intervals for recall and precision in Section \ref{SEI-sensitivity} simulation}
%		\label{fig:SEI_eval}
%	\end{center}
%\end{figure}
%
%  \begin{figure}[hbt]
%	\centering
%	\begin{subfigure}{0.4\textwidth}
%		\includegraphics[width=\textwidth]{../SEI_sensitivity/Z_plot} 
%		\caption{}\label{fig:SEI-Z}
%	\end{subfigure}\hspace{\columnsep}%
%	\begin{subfigure}{0.4\textwidth}
%		\includegraphics[width=\textwidth]{../SEI_sensitivity/eval_plot} 
%		\caption{}\label{fig:SEI-eval}
%	\end{subfigure}
%\caption{Simulation results Section \ref{SEI-sensitivity}. In \ref{fig:SEI-Z}, 
%\end{figure}
%Figure \ref{fig:here}

@@

	%We also compute a partial estimate of the linkage structure, using $\theta_{10} = \theta_{01} = 1$, $\theta_{11} = 2$, and $\theta_R = 0.1$ as in the simulation study in Appendix \ref{partial}. Here, the Bayes estimate provides 136 matches of which the model is quite confident, and 175 records to verify manually. This means that after clerical review, the number of individuals replicated across data files would fall in the interval (136, 311), encapsulating the posterior credible interval. More or fewer records could be identified for clerical review by decreasing or increasing $\theta_R$.

	%and a range of (140, 294) after the partial estimate and clerical review.

@@

%	\section{Appendix}
%	\label{sec:appendix}

>>>>

\begin{abstract} 
Within the field of record linkage, Bayesian methods have the crucial advantage of quantifying uncertainty from imperfect linkages. However, current implementations of Bayesian Fellegi-Sunter models are computationally intensive, making them challenging to use on larger-scale record linkage tasks. To address these computational considerations, we propose fast beta linkage (\texttt{fabl}), an extension to the Beta Record Linkage (\texttt{BRL}) method of \cite{sadinle_bayesian_2017}. Specifically, we use independent prior distributions over the matching space, allowing us to use hashing techniques that reduce computational overhead. This also allows us to complete pairwise record comparisons over large data files through parallel computing and to reduce memory costs through a new technique called storage efficient indexing. Through simulations and two case studies, we show that \texttt{fabl} can have markedly increased speed with minimal loss of accuracy when compared to \texttt{BRL}.
\end{abstract}

%% ** Keywords **
\begin{keyword}
\kwd{bipartite record linkage}
\kwd{entity resolution}
\kwd{data cleaning}
\kwd{parallelization}
\kwd{hashing}
\end{keyword}

@@

@@

@@

@@

@@

@@

@@

\begin{subequations}
\begin{align}
	\mathcal{L}(\bm{Z}, \bm{m}, \bm{u} \mid \gamma) &= \prod_{i=1}^{n_A}  \prod_{j=1}^{n_B}\prod_{f=1}^{F}\prod_{l=1}^{L_f}\left[  m_{fl}^{I(Z_j = i)}u_{fl}^{I(Z_j \neq i)}\right]^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}, \label{eqn:likelihood}\\
	\bm{m}_f &\sim \text{Dirichlet}(\alpha_{f1}, \ldots, \alpha_{f L_f}), \forall f = 1, \ldots, F, \label{eqn:m} \\
	\bm{u}_f &\sim \text{Dirichlet}(\beta_{f1}, \ldots, \beta_{f L_f}),\forall f = 1, \ldots, F,  \label{eqn:u}\\
	p(Z_j = q| \pi)  &=
	\begin{cases} 
		\frac{1}{n_A}\pi,  & q \leq n_A; \\
		1-\pi, &  q  = n_A + j; \\
	\end{cases} \label{eqn:z}\\
	\pi &\sim \text{Beta}(\alpha_{\pi}, \beta_{\pi})\label{eqn:pi}.
\end{align}
\end{subequations}

We estimate the posterior distribution of the parameters in (\ref{eqn:likelihood} - \ref{eqn:pi}) using a Gibbs sampler. We initialize $\bm{m}$ and $\bm{u}$ from random draws from their prior distributions, and initialize $\bm{Z}$ to reflect no matches across data files; that is, $\bm{Z} = (n_A + 1, \ldots, n_A + n_B)$. To take the $(s+1)$th sample of each $\bm{m}_f$ and $\bm{u}_f$ given $\bm{Z}^{(s)}$, we use the full conditionals,
\begin{subequations}
\begin{align}
	\bm{m}_f^{(s+1)}|\gamma, \bm{Z}^{(s)} &\sim \text{Dirichlet}(\alpha_{f1}(\bm{Z}^{(s)}), \ldots, \alpha_{fL_f}(\bm{Z}^{(s)})), \label{eqn:m_update} \\
	\bm{u}_f^{(s+1)}|\gamma, \bm{Z}^{(s)} &\sim \text{Dirichlet}(\beta_{f1}(\bm{Z}^{(s)}), \ldots, \beta_{fL_f}(\bm{Z}^{(s)})), \label{eqn:u_update} \\
	\text{where }\alpha_{fl}(\bm{Z}^{(s)})&= \alpha_{fl} + \sum_{i=1}^{n_A}\sum_{j=1}^{n_B} I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} = i), \label{eqn:alpha_update} \\
	\text{and } \beta_{fl}(\bm{Z}^{(s)})&=  \beta_{fl} + \sum_{i=1}^{n_A}\sum_{j=1}^{n_B}  I_{obs}(\gamma_{ij}^f) I(\gamma_{ij}^f = l) I(Z_j^{(s)} \neq i) \label{eqn:beta_update}.
\end{align}
\end{subequations}
Next, the full conditional for $\pi$ is given by
\begin{align}
	\pi^{(s+1)}|\bm{Z}^{(s)},  \alpha_{\pi}, \beta_{\pi}, \pi \sim  \text{Beta}(n_{AB}(\bm{Z}^{(s)}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}^{(s)}) + \beta_{\pi}).
\end{align}
where $n_{AB}(\bm{Z}^{(s)}) = \sum_{j=1}^{n_B} I(Z_j^{(s)} \leq n_A)$.

Lastly, we sample $\bm{Z}$ componentwise from the full conditional for each $Z_j$:
\begin{align}
	\label{eqn:z_full_conditional}
	p\left(Z_j^{(s+1)}  = q|\gamma, \bm{m}^{(s+1)}, \bm{u}^{(s+1)},  \pi^{(s+1)}\right) \propto
	\begin{cases} 
		\frac{\pi^{(s+1)}}{n_A} w_{qj}^{(s+1)},  & q \leq n_A; \\
		1 - \pi^{(s+1)}, & q  = n_A + j, \\
	\end{cases}
\end{align}

where, for all $i \in \{1, \ldots, n_A\}$ and $j \in \{1, \ldots, n_B\}$, 
\begin{align}
	\label{eqn:fs_weight}
	w_{ij}^{(s)} = \prod_{f=1}^{F}\prod_{l = 1}^{L_f} \left(\frac{m_{fl}^{(s)}}{u_{fl}^{(s)}}\right)^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}.
\end{align}
Derivations for these full conditionals can be found in Appendix \ref{app:derivations}.

@@

With \texttt{fabl}, we introduce two techniques to further expand the scalability of probabilistic record linkage. First, we propose hashing methods that allow us to compute summary statistics that reduce the computational complexity of the Gibbs sampler and the memory requirements of the storing the comparison vectors. Second, we introduce storage efficient indexing, which reduces the memory costs associated with unlikely matches.

@@

We then map these integers to sequential integers $\{1, \ldots, P\}$. We refer to each unique agreement pattern as $h_p$, and to the set of unique agreement patterns as $\mathcal{P} = \{h_1, \ldots, h_P\}$. When the $(i,j)$ record pair exhibits agreement pattern $p$, we say $\gamma_{ij} = h_p$. In calculations, we will at times use the one-hot encoding of agreement pattern $h_p$, denoted $e(h_p)$. This is a vector of length $\sum_{f=1}^F L_f$ in which the $l + \sum_{k=1}^{f-1} L_k$ component is 1 when $\gamma_{ij}^f = l$, and 0 otherwise.

@@

		For linkage tasks with large amounts of records, we can partition $A$ and $B$ into $t_A$ and $t_B$ smaller disjoint chunks for more manageable computations. Let $\{A^1, \dots, A^{t_A}\}$ be a partition of $A$ such that $\cup_{a=1}^{t_A} A^a = A$ and $A^a \cap A^{a'}=\emptyset$ for all $a \neq a'$.  Likewise, let $\{B^1, \dots, B^{t_b}\}$ be a partition of $B$ such that $\cup_{b=1}^{t_B} B^b = B and B^b \cap B^{b'}=\emptyset$ for all $b \neq b'$.  For example, if $n_A = n_B = 50000$ and $t_A = t_B = 100$, each $A^a$ and $B^b$ would contain disjoint sets of 500 records. For each $A^a$, we conduct all-to-all comparisons with each $B^b$ to construct the comparison matrix $\gamma^{ab}$.

		\textcolor{teal}{Then, we} conduct hashing, obtain the compressed \textcolor{teal}{comparison vectors} $\tilde{\gamma}^{ab}$, and \textcolor{teal}{remove}
		the 
\textcolor{teal}{memory-intensive}
		\textcolor{teal}{comparison vectors} $\gamma^{ab}$ 
		before continuing with the next chunk of data. 
		In detail, we calculate
\begin{subequations}
	\begin{align}
		r_{p_j}^{ab} &= \{i \in 1, \dots, n_A| \gamma_{ij} = h_p, j \in B^b\}, \label{r_{p_j}^{ab}} \\
		N_{p_j}^{ab} &= |r_{p_j}^{ab}|. \label{N_{p_j}^{ab}}
	\end{align}
\end{subequations}
These can computed serially or in parallel. Summary statistics from each pairwise chunk comparison can be synthesized to recover summary statistics for the full comparison matrix $\gamma$ through
\begin{subequations}
	\begin{align}
		r_{p_j} &= (r_{p_j}^{11}, \ldots, r_{p_j}^{ t_A t_B}) \text{ for } a = 1, \ldots, t_A \text{ and } b = 1, \ldots, t_B, \label{r_{p_j}} \\
		N_{p_j} &= \sum_{a = 1}^{t_A} \sum_{b = 1}^{t_B} N_{p_j}^{ab}.\label{N_{p_j}}	\end{align}
\end{subequations}

@@

@@

Although the figures suggest that $S=2$ is adequate for maintaining linkage performance, we suggest a more conservative value like $S=10$. When evaluating the performance of a record linkage algorithm, researchers often examine posterior probabilities. By concentrating probability mass on arbitrary nonmatches, low values of $S$ may induce suspiciously high posterior probability for certain record pairs, providing a misleading perception of model performance.

@@

@@
